---
title: "GSS challange More Data"
author: "Chris Gonzalez"
date: "July 3,2023"
output: html_document
---







```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS2016.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,cappun)
mydata <- na.omit(mydata)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

Is attitude toward capitol punishment (cappun) independent of race (race)?
If not, then whose view differs from whom??

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~race + cappun,data=mydata)
barchartGC(~race + cappun,data=mydata, type="percent")

```


According to the data presented, the chart indicates that there exists a higher degree of support for capital punishment among individuals who identify as white, while black individuals oppose, displaying a general opposition to the concept. Moreover, the chart suggests that there are also other segments of the population who align with the perspective favoring capital punishment among all that where surveyed.



## Now with The Most data (fewer variables gives more data points)



### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table1 <- xtabs(~race + cappun, data=mydata)
rowPerc(table1)
colPerc(table1)
```

Analyzing the first table, it can be observed that among the white population, 65.10% express favor for capital punishment, while 34.90% hold an opposing stance. Similarly, among the black population, 42.63% oppose capital punishment, whereas 57.37% express favor for it. Among individuals categorized as "other," 55.20% are in favor, while 44.80% oppose capital punishment. The second chart further demonstrates this by saynig 79.80% white are in favor of capital punishment, 24% black oppose and other category 8.47 oppose. 

## Now with More data



## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

The data presented demonstrates a significant relationship with a p-value of less than 2.2e-16, indicating a highly statistically significant result. This suggests that there is strong evidence to support the presence of an association or difference among the variables being examined.


```{r}
fisherXY(mydata$race,mydata$cappun)
```
The analysis reveals that there are distinct differences among the various racial groups, namely white, black, and other, regarding their opinions on capital punishment. Specifically, when comparing white and black respondents, a highly significant difference is evident, with a p-value of less than 2.2e-16. This extremely low p-value indicates a substantial disparity in opinions between these two groups with white group in favor of capital punishment. When comparing white respondents to those classified as "other," the obtained p-value is 0.002607, signifying a statistically significant distinction in perspectives. Similarly, when comparing black respondents to those categorized as "other," the p-value of 0.001564 also highlights a significant contrast in opinions between these groups with "other" more in favor of capital punishment.These findings underscore the noteworthy variations in attitudes towards capital punishment observed across different racial groups, further supporting the significance of these observed differences in the data.


## More data version


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
